Figures

### 2019-12-13 manuscript/figures.Rmd

grid.arrange(PDI_response_surfaces$`a)`,PDI_response_surfaces$`b)`,PDI_response_surfaces$`c)`,PDI_response_surfaces$legend,nrow = 2,newpage = F)
```

@@

grid.arrange(DAI_response_surfaces$`a)`,DAI_response_surfaces$`b)`,DAI_response_surfaces$`c)`,DAI_response_surfaces$`d)`,DAI_response_surfaces$`e)`,DAI_response_surfaces$`f)`,DAI_response_surfaces$legend,ncol = 3,layout_matrix = rbind(c(1,4,7),c(2,5,7),c(3,6,7)),widths = c(4,4,1),newpage = F)
```

>>>>

grid.arrange(PDI_response_surfaces$`a)`,
             PDI_response_surfaces$`b)`,
             PDI_response_surfaces$`c)`,
             PDI_response_surfaces$legend,
             nrow = 2,newpage = F)
```

@@

grid.arrange(textGrob(expression(bold('AOD')),hjust = -0.1),
             textGrob(expression(bold('COD')),hjust = -0.1),
             textGrob(expression(bold('Neutral')),rot = 90,hjust = -0.1),
             textGrob(expression(bold('Moderate')),rot = 90,hjust = -0.1),
             textGrob(expression(bold('Severe')),rot = 90,hjust = -0.1),
             DAI_response_surfaces$`a)`,
             DAI_response_surfaces$`b)`,
             DAI_response_surfaces$`c)`,
             DAI_response_surfaces$`d)`,
             DAI_response_surfaces$`e)`,
             DAI_response_surfaces$`f)`,
             DAI_response_surfaces$legend,
             ncol = 4,
             layout_matrix = rbind(c(NA,1,2,NA),c(3,6,9,12),c(4,7,10,12),c(5,8,11,12)),
             widths = c(1,10,10,2),
             heights = c(1,10,10,10),
             newpage = F)
```
